\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-17 design.tex
more dave revisions

\begin{itemize}
	\item {\bf Decision point selection.} Landslide provides an interface for the user to manually limit identification of decision points to only ``relevant'' modules of the kernel, thereby only generating thread interleavings around points within those modules.
	\item {\bf Memory conflict selection.} Landslide also provides a mechanism for ignoring shared memory conflicts on certain common data structures (especially those accessed in every thread transition, such as the scheduler queues), to enable DPOR to achieve greater reduction. Intuitively, this represents sacrificing the ability to find races around those data structures to make searching other components more feasible.
\end{itemize}

>>>>

\begin{itemize}
	\item {\bf Iterative refinement of interleaving granularity.} The recommended usage pattern is to begin by searching state spaces with coarse-grained interleavings, and then refining the decision set afterwards until bugs are found. Landslide automatically identifies a ``minimal decision set'', comprising only voluntary reschedules (Section~\ref{sec:components-arbiter}), to use as the coarsest granularity.
	\item {\bf Decision point selection.} Landslide provides an interface for the user to manually limit identification of decision points to only ``relevant'' modules of the kernel, thereby only generating thread interleavings around points within those modules.
	\item {\bf Memory conflict selection.} Landslide also provides a mechanism for ignoring shared memory conflicts on certain common data structures (especially those accessed in every thread transition, such as the scheduler queues), to enable DPOR to achieve greater reduction. Intuitively, this represents sacrificing the ability to find races around those data structures to make searching other components more feasible.
\end{itemize}

### 2012-05-17 futurework.tex
more dave revisions

Simics's convenient bookmarking mechanism will be no more in virtual-machine-land. One possibility for backtracking would be to record-and-replay the events of each branch (up to the point at which Landslide chooses to have decided differently), restarting the system's execution from the beginning each time. Another option might be to snapshot the state of the kernel at each decision point, and use those to resume without re-executing everything from the beginning (kernel boot-up and initialisation is much more expensive than individual system calls, after all).

>>>>

Simics's convenient bookmarking mechanism will be no more in virtual-machine-land. One possibility for backtracking would be to record-and-replay the events of each branch (up to the point at which Landslide chooses to have decided differently), restarting the system's execution from the beginning each time. Another option might be to snapshot the state of the kernel (and associated devices) at each decision point, and use those to resume without re-executing everything from the beginning (kernel boot-up and initialisation is much more expensive than individual system calls, after all).

### 2012-05-17 using.tex
more dave revisions

@@

>>>>

The recommended ``attack plan'' for using Landslide corresponds directly to the sections in this chapter. Section~\ref{sec:using-requirements} lists the requirements a kernel must fulfill to be compatible with Landslide. Section~\ref{sec:using-instrumenting} describes the process of instrumenting a kernel, which involves annotating the kernel, filling out a configuration file, and instrumenting within Landslide itself. Section~\ref{sec:using-customise} describes ways to configure Landslide's behaviour to help focus its search for bugs.

@@

In addition to meeting the Pebbles specifcation for 15-410, there are some additional restrictions that Landslide imposes, some inherent to its testing model, and others as artifacts of its interface/implementation.
